---
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning = F)
```

```{r libraries & data, include = F}
require(ggplot2)
require(data.table)

load("../data/experiment_3.rdata") #Created in data_import
```

# Experiment 3 

## KNMI station vs. KNMI radar vs. GPM-IMERG satellite over Netherlands

### Introduction

This is a presentation of the scalegram methodology, applied for the validation of satellite precipitation product. Here, we use the [GPM IMERGHH data product](https://disc.gsfc.nasa.gov/datasets/GPM_3IMERGDF_V05/summary) and the KNMI radar, the dense precipitation network of KNMI for Netherlands.

***

### Data

**Satellite data (gpm)**

* Dataset: GPM IMERG Final Precipitation 
* Temporal Resolution: 1 day
* Spatial Resolution: 0.1 deg
* Date Range: `r min(gpm_d_prcp$time)` to `r max(gpm_d_prcp$time)` 
* Spatial Region: latitude: `r range(gpm_d_cells$lat)`, longitude: `r range(gpm_d_cells$lon)`
* Variables: precipitationCal
* Format: netCDF 4
* Variables: gpm_d_cells (coordinates) & gpm_d_prcp (values) in _experiment_3.rdata_.
* IDs: `r min(gpm_d_cells$id)`
* Size: `r nrow(gpm_d_prcp)` total values, over `r nrow(gpm_d_cells)` grid cells
* Downloaded from: https://climexp.knmi.nl/select.cgi?id=312456c83e660703df1bfea9ba4fba50&field=imerg_daily 

**Instrumental data (knmi)**

todo
* Downloaded from: https://climexp.knmi.nl/PhomNL.cgi?id=312456c83e660703df1bfea9ba4fba50

**Radar data (knmi)**

todo
* Downloaded from: https://climexp.knmi.nl/select.cgi?id=312456c83e660703df1bfea9ba4fba50&field=knmi_radar_daily

***

### Code structure

_data_import.R_ : Import and prepare station, radar and satellite data for netherlands. Each pair 
# of data (values and coordinates) is then saved to experiment_3.rdata.

_spatial_agg.R_ : Aggregation of rain events over space.

***

### Datasets in space

In each case, grid cells with no gauge/radar cell center within a 0.5 deg radious of satellite cell center, are removed.

**GPM grid cell centers vs. station locations**

```{r plot stations/grid cells, eval = T}
my_date <- as.Date("2016-9-03")
test_rdr <- rdr_prcp[time == my_date]
test_rdr <- merge(test_rdr, rdr_cells)

test_gpm <- gpm_d_prcp[time == my_date]
test_gpm <- merge(test_gpm, gpm_d_cells)

test_knmi <- knmi_prcp[time == my_date]
test_knmi <- merge(test_knmi, knmi_stations)
test_knmi <- test_knmi[complete.cases(test_knmi)]

ggplot(test_rdr, aes(y = lat, x = lon, col = prcp)) + 
  geom_point(data = test_gpm[id %in% knmi_stations$nearest_cell], aes(y = lat, x = lon, size = prcp), col = "red") +
  geom_point(data = test_knmi, aes(y = lat, x = lon, size = prcp), col = "yellow") +
  labs(x = NULL, y = NULL) +
  theme_bw()
```

**GPM grid cell centers vs. radar cells**

```{r plot radar/grid cells, eval = T}
ggplot(test_rdr, aes(y = lat, x = lon, col = prcp)) + 
  geom_point() +
  geom_point(data = test_gpm[id %in% rdr_cells$nearest_cell], aes(y = lat, x = lon, size = prcp), col = "red") +
  labs(x = NULL, y = NULL) +
  theme_bw()
```

The figures above present daily precipitation on `r my_date`. 

***

**Monthly heterogeneity**
```{r plot monthly means, eval = F}
noa_month_prcp <- noa_prcp[, sum(prcp, na.rm = T), id]  
colnames(noa_month_prcp)[2] <- "prcp"
gpm_month_prcp <- gpm_d_prcp[, sum(prcp), id]
colnames(gpm_month_prcp)[2] <- "prcp"

noa_month_prcp <- merge(noa_month_prcp, noa_stations[, .(id, lon, lat)])
gpm_month_prcp <- merge(gpm_month_prcp, gpm_cells[, .(id, lon, lat)])

month_prcp <- rbind(cbind(gpm_month_prcp, dataset = "gpm"),
                    cbind(noa_month_prcp, dataset = "noa"))

ggplot(data = month_prcp, aes(lon, lat, col = prcp, size = dataset)) +
  geom_point() +
  xlab(label = "") +
  ylab(label = "") +
  theme_bw()
```


