---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning = F)
```

```{r libraries & data}
require(ggplot2)
require(data.table)

load("../data/experiment_3.rdata") #Created in data_import
```

# Experiment 3 

## KNMI station vs. KNMI radar vs. GPM-IMERG satellite over Netherlands

### Introduction

This is a presentation of the scalegram methodology, applied for the validation of satellite precipitation product. Here, we use the [GPM IMERGHH data product](https://disc.gsfc.nasa.gov/datasets/GPM_3IMERGDF_V05/summary) and the KNMI radar, the dense precipitation network of KNMI for Netherlands.

### Data

**Satellite data (gpm)**

* Dataset: GPM IMERG Final Precipitation 
* Temporal Resolution: 1 day
* Spatial Resolution: 0.1 deg
* Date Range: `r min(gpm_d_prcp$time)` to `r max(gpm_d_prcp$time)` 
* Spatial Region: latitude: `r range(gpm_d_cells$lat)`, longitude: `r range(gpm_d_cells$lon)`
* Variables: precipitationCal
* Format: netCDF 4
* Variables: gpm_d_cells (coordinates) & gpm_d_prcp (values) in _experiment_3.rdata_.
* IDs: `r min(gpm_d_cells$id)`
* Size: `r nrow(gpm_d_prcp)` total values, over `r nrow(gpm_d_cells)` grid cells

**Instrumental data (knmi)**

todo

**Radar data (knmi)**

todo

### Code structure

_data_import.R_ : Import and prepare station, radar and satellite data for netherlands. Each pair 
# of data (values and coordinates) is then saved to experiment_3.rdata.

_spatial_agg.R_ : Aggregation of rain events over space.

**Grid cell centers vs. Stations locations**

All grid cells with no gauge closer than 0.5 deg are removed.

```{r plot stations/grid cells, eval = F}
noa_locations <- noa_stations[, c(1, 3, 4, 6)]
noa_locations$dataset <- factor("noa")
gpm_locations <- gpm_cells[id %in% noa_stations$nearest_cell]
gpm_locations$nearest_cell <- gpm_locations$id
gpm_locations$dataset <- factor("gpm")
all_locations <- rbind(noa_locations, gpm_locations)
ggplot(data = all_locations, aes(lon, lat, size = dataset, col = nearest_cell)) +
  geom_point() +
  xlab(label = "") +
  ylab(label = "") +
  theme_bw()
```

**Monthly heterogeneity**

```{r plot monthly means, eval = F}
noa_month_prcp <- noa_prcp[, sum(prcp, na.rm = T), id]  
colnames(noa_month_prcp)[2] <- "prcp"
gpm_month_prcp <- gpm_d_prcp[, sum(prcp), id]
colnames(gpm_month_prcp)[2] <- "prcp"

noa_month_prcp <- merge(noa_month_prcp, noa_stations[, .(id, lon, lat)])
gpm_month_prcp <- merge(gpm_month_prcp, gpm_cells[, .(id, lon, lat)])

month_prcp <- rbind(cbind(gpm_month_prcp, dataset = "gpm"),
                    cbind(noa_month_prcp, dataset = "noa"))

ggplot(data = month_prcp, aes(lon, lat, col = prcp, size = dataset)) +
  geom_point() +
  xlab(label = "") +
  ylab(label = "") +
  theme_bw()
```


