---
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning = F)
```

```{r libraries & data, include = F}
require(ggplot2)
require(data.table)

load("../data/experiment_3_raw.rdata") #Created in data_import
```

# Experiment 3 

## KNMI station vs. KNMI radar vs. GPM-IMERG satellite over Netherlands

### Introduction

This is a presentation of the scalegram methodology, applied for the validation of satellite precipitation product. Here, we use the [GPM IMERGHH data product](https://disc.gsfc.nasa.gov/datasets/GPM_3IMERGDF_V05/summary) and the KNMI radar, the dense precipitation network of KNMI for Netherlands.

***

### Data

**Satellite data (gpm)**

* Dataset: GPM IMERG Final Precipitation 
* Temporal Resolution: 1 day
* Spatial Resolution: 0.1 deg
* Date Range: `r min(gpm_d_prcp$time)` to `r max(gpm_d_prcp$time)` 
* Spatial Region: latitude: `r range(gpm_d_cells$lat)`, longitude: `r range(gpm_d_cells$lon)`
* Variables: precipitationCal
* Format: netCDF 4
* Variables: gpm_d_cells (coordinates) & gpm_d_prcp (values) in _experiment_3.rdata_.
* IDs: `r min(gpm_d_cells$id)`
* Size: `r nrow(gpm_d_prcp)` total values, over `r nrow(gpm_d_cells)` grid cells
* Downloaded from: https://climexp.knmi.nl/select.cgi?id=312456c83e660703df1bfea9ba4fba50&field=imerg_daily 

**Instrumental data (knmi)**

* Dataset: 240 homogenised stations 1951-now (raw)
* Temporal Resolution: 24hours
* Spatial Resolution: -
* Date Range: `r min(knmi_prcp$time)` to `r max(knmi_prcp$time)` 
* Spatial Region: latitude: `r range(knmi_stations$lat)`, longitude: `r range(knmi_stations$lon)`
* Format: *.txt
* IDs: `r min(knmi_stations$id)`
* Size: `r nrow(knmi_prcp)` total values, over `r nrow(knmi_stations)` stations
* Downloaded from: https://climexp.knmi.nl/PhomNL.cgi?id=312456c83e660703df1bfea9ba4fba50

**Radar data (knmi)**

* Dataset: RAD_NL25_RAC_MFBS_24H_NC
* Temporal Resolution: 24hours
* Spatial Resolution: 1x1km
* Date Range: `r min(rdr_prcp$time)` to `r max(rdr_prcp$time)` 
* Spatial Region: latitude: `r range(rdr_cells$lat)`, longitude: `r range(rdr_cells$lon)`
* Format: *.nc
* Variables: 
* IDs: `r min(rdr_cells$id)`
* Size: `r nrow(rdr_prcp)` total values, over `r nrow(rdr_cells)` grid cells
* Downloaded from: https://climexp.knmi.nl/select.cgi?id=312456c83e660703df1bfea9ba4fba50&field=knmi_radar_daily

***

### Code structure

_data_import.R_ : Import and prepare station, radar and satellite data for the Netherlands. Each pair 
of data (values and coordinates) is then saved to **experiment_3_raw.rdata**.

_comparison_prep.R_ : Prepare datasets for comparison: align datasets in time and space and save them to **experiment_3_main.rdata**, find wet days
and save them to **experiment_3_wdays.rdata**.

_comparison_eda.R_ : Exploratory analysis contains comparison of first moments, extreme values (gumbel probability), wet days (intersection plots). 

_comparison_agg.R_ : Aggregation of rain events over space and time.

***

### Exploratory Data Analysis

_Results of comparison_eda.R_

```{r EDA}

```


