---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, warning = F)
```

```{r libraries & data}
require(ggplot2)
require(data.table)

load("../data/experiment_1.rdata") #Created in data_import
```

# Experiment 1 

## NOA station vs. GPM-IMERG satellite over Attiki (Greece)

### Introduction

This is a presentation of the scalegram methodology, applied for the validation of satellite precipitation product. Here, we use the [GPM IMERGHH data product](https://disc.gsfc.nasa.gov/datasets/GPM_3IMERGHH_05/summary) and the dense precipitation network of National Observatory of Athens for Attiki (Greece) region.

### Data

**Satellite data (gpm)**

* Dataset: GPM IMERG Final Precipitation L3 Half Hourly 0.1 degree x 0.1 degree V05
* Date Range: 2017-11-30 to 2017-12-31
* Spatial Region 23.269, 37.786, 23.906, 38.467
* Variables: precipitationCal
* Format: netCDF 4

The data were cropped to [2017-12-01, 2017-12-31] period. Then all grid cells with no gauge closer than 0.5 deg were removed.

Right now working with the 1d product downloaded from knmi, which does not correspond to the 30-min. Have to check code and version.

**Instrumental data (noa)**

* Dataset: NOA automatic precipitation network
* 10 minute precipitation 
* Date Range: 2017-12-01, 2017-12-31
* Spatial Region 23.269, 37.786, 23.906, 38.467
* Variables: rainfall
* Format: txt

Stations above 400 meters were removed.

**Grid cell centers vs. Stations locations**

```{r plot stations/grid cells}
noa_locations <- noa_stations[, c(1, 3, 4, 6)]
noa_locations$dataset <- factor("noa")
gpm_locations <- gpm_cells[id %in% noa_stations$nearest_cell]
gpm_locations$nearest_cell <- gpm_locations$id
gpm_locations$dataset <- factor("gpm")
all_locations <- rbind(noa_locations, gpm_locations)
ggplot(data = all_locations, aes(lon, lat, size = dataset, col = nearest_cell)) +
  geom_point() +
  xlab(label = "") +
  ylab(label = "") +
  theme_bw()
```

**Monthly heterogeneity**

```{r plot monthly means}
noa_month_prcp <- noa_prcp[, sum(prcp, na.rm = T), id]  
colnames(noa_month_prcp)[2] <- "prcp"
gpm_month_prcp <- gpm_d_prcp[, sum(prcp), id]
colnames(gpm_month_prcp)[2] <- "prcp"

noa_month_prcp <- merge(noa_month_prcp, noa_stations[, .(id, lon, lat)])
gpm_month_prcp <- merge(gpm_month_prcp, gpm_cells[, .(id, lon, lat)])

month_prcp <- rbind(cbind(gpm_month_prcp, dataset = "gpm"),
                    cbind(noa_month_prcp, dataset = "noa"))

ggplot(data = month_prcp, aes(lon, lat, col = prcp, size = dataset)) +
  geom_point() +
  xlab(label = "") +
  ylab(label = "") +
  theme_bw()
```


